A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by organization x.}

### 2021-09-02 paper.tex
Draft update
Work in progress
Draft Update
Paper updated to be as close as possible to the presentation.

One of the publications with the most influence and impact on our research,
which inspired us to carry out this project is "A container-based cloud-native
architecture for the reproducible execution of multi-population optimization
algorithms" by Mario García Valdez and Juan J. Merelo Guervós.

They propose a cloud-native optimization framework, that can include multiple
(population-based) algorithms without increasing the number of parameters that
need tuning. Their solution can support different algorithms at the same time,
work asynchronously, and also be readily deployable to any cloud platform.

"Splitting a population into multiple instances is a technique used extensively
in recent years to help improve the performance of nature-inspired optimization
algorithms. Work on those populations can be done in parallel, and they can
interact asynchronously, a fact that can be leveraged to create scalable
implementations based on, among other methods, distributed, multi-threaded,
parallel, and cloud-native computing". [All of the above taken from their publication]

[Note: This draft is a work in progress, needs improvement]

@@

From the ground up, we designed the algorithm as a cloud-native solution using
the cloud available resources to divide the processing workload, among several
computers or running the algorithm as a cloud service. The algorithm works
concurrently and asynchronously on a constantly evolving population, using
different computers (or containers) independently, eliminating waiting times
between processes.

In this paper, we present an algorithm inspired by the biological life-cycle of
animal species, which consists of several stages: birth, growth, reproduction,
and death. As in nature, we intend to execute all these stages in parallel and
asynchronously on a population that evolves constantly. This algorithm starts
with a randomly generated population, where the processes will interact with
the population independently. This means that at any given time, any individual
can experience any of these processes.

@@

Similar to a GA, our algorithm starts with the process responsible for the
random generation of individuals. In our scheme, we call it birth, however, we
must mention that the successful reproduction process will result in the birth
of new individuals (offspring).

@@

The attraction of a couple will depend on fitness: the better individual's
fitness, the more attractive it will be, making it easier to find mating
matches. Not all couples will be compatible, so reproduction will not always be
possible, but the problem arises: how to quantify the attraction between two
individuals?. The reproduction process will be taking random pairs of
individuals to evaluate their attraction as a couple, to try to breed; when the
gestation is successful, a new pair of individuals will be born (as the
offspring).

@@

The process of dying represents the challenges and adversities that life
presents (to overcome). This process evaluates the individual resistance to
survive in the environment. The better fitness the individual has will increase
its chances of survival. As time progresses, the demands of nature will also
increase, pushing for only the best individuals to survive.

\section{Experimental}

@@

\section{Results}

@@

In this research, we were able to demonstrate that it is possible to evolve a
population of individuals, similar to a Genetic Algorithm (GA), using a
distributed, parallel, and asynchronous methodology.

We implemented the algorithm with Docker containers by solving the OneMax
problem comparing it with a traditional (sequential) GA algorithm, where it
showed favorable and promising results. To further validate this work we could
use control or something more complex and demanding problem that requires to
compute real numbers.

>>>>

\subsection{Background}

One of the publications with the most influence on our research proposes a
cloud-native optimization framework, that can include multiple
(population-based) algorithms [1]. In their research, they work with ideas such
as:

These ideas planted the seed of thought in our current presentation.

@@

From the ground up, we designed the algorithm as a cloud-native solution using
the cloud available resources to divide the processing workload, among several
computers or running the algorithm as a cloud service. [The algorithm works
concurrently and asynchronously on a constantly evolving population, using
different computers (or containers) independently, eliminating waiting times
between processes.]

In this paper, we present an algorithm inspired by the biological life-cycle of
animal species, which consists of several stages: birth, growth, reproduction,
and death. As in nature, we intend to execute all these stages in parallel and
asynchronously on a population that evolves constantly.

@@

This algorithm starts with a randomly generated population, where the processes
will interact with the population independently. This means that at any given
time, any individual can experience any of these processes. Birth is the first
process of our algorithm, and it is responsible for the initial generation of
individuals.

@@

The attraction of a couple will depend on fitness: the better individual's
fitness, the more attractive it will be, making it easier to find mating
matches. Not all couples will be compatible, so reproduction will not always be
possible, but the problem arises: how to quantify the attraction between two
individuals?. This process will be taking random pairs of individuals to
evaluate their attraction as a couple, to try to breed; when the gestation is
successful, a new pair of individuals will be born (as the offspring).

@@

The death stage represents the challenges and adversities that life presents
(to overcome). This process evaluates the individual resistance to survive in
the environment. The better fitness the individual has will increase its
chances of survival. As time progresses, the demands of nature will also
increase, pushing for only the best individuals to survive.

\section{Experiments}

@@

\subsection{Experimental Setup}

\subsection{Results}

\section{Discussion}

@@

We implemented the algorithm with Docker containers by solving the OneMax
problem comparing it with a traditional (sequential) GA algorithm, where it
showed favorable and promising results. To further validate this work, we could
use control or some more complex and demanding problem that requires computing
real numbers.

As the complexity of problems increases, it is essential to have a scalable,
replicable, and fault-tolerant model that uses collaborative techniques to work
in the cloud, where multiple resources will be communicating asynchronously.
This research has shown that it is possible to evolve a population of
individuals, similar to a Genetic Algorithm (GA), using a distributed,
parallel, and asynchronous methodology.
